``Colloidal rain'' as a novel route to crystallization via viscoelastic phase separation

### 2015-10-13 crystal-gel/science/crystal_gel_letter2.tex
Small change.

In the next section we demonstrate that the volume growth is due to direct condensation of the gas phase on the crystalline seeds.
First we show in Fig.~\ref{fig:transitions}A slabs of 10 particle diameter thickness for configurations at $\phi\approx 0.30$ and $c_p=0.38$ mg/g at different times.
Particles are colored according to their phase. The figure shows the first nucleation
events inside the liquid network (left panel); then these crystalline nuclei grow directly from the gas phase (middle panel), and finally
the different nuclei coalesce (right panel).

>>>>

In the next section we demonstrate that the volume growth is due to direct condensation of the gas phase on the crystalline seeds.
Supplementary Movie 2 shows the confocal microscopy video for the crystallizing sample at $\phi\approx 0.30$ and $c_p=0.38$ mg/g,
where the process of crystal growth by direct attachment of gas particles can be observed directly.
From the trajectory, we extract slabs of 10 particle diameter thickness for configurations at $\phi\approx 0.30$ and $c_p=0.38$ mg/g at different times,
shown in Fig.~\ref{fig:transitions}A slabs.
Particles are colored according to their phase. The figure shows the first nucleation
events inside the liquid network (left panel); then these crystalline nuclei grow directly from the gas phase (middle panel), and finally
the different nuclei coalesce (right panel).
